R Notebook

### 2017-03-31 doc/RMD/MLG-distribution.Rmd
update friggen final graph

```{r}
make_from_to <- function(poplist){
  x <- combn(poplist, 2)
  tibble::data_frame(from = x[1, ], to = x[2, ])
}
crosses <- mlg.crosspop(dat, df = TRUE, quiet = TRUE)

@@

```{r}

@@

apply(pops, 1, function(i){
    plot(i$graph, 
         layout = layout_as_star(i$graph, center = i$Population), 
         main = i$Population, 
         vertex.size = psize[names(V(i$graph))])
  })
par(mfrow = c(1, 1))
do.call("union", pops$graph) %>% 
  plot(., vertex.size = psize[names(V(.))],
       layout = layout_as_star(., center = "MI"))
```

>>>>

```{r, fig.width = 10, fig.height = 10}
make_from_to <- function(poplist){
  x <- combn(poplist, 2)
  tibble::data_frame(from = x[1, ], to = x[2, ])
}
crosses <- mlg.crosspop(dat, df = TRUE, quiet = TRUE)

@@

```{r, fig.width = 10, fig.height = 10}

@@

apply(pops, 1, function(i){
    plot(i$graph, 
         layout = layout_as_star(i$graph, center = i$Population), 
         main = i$Population, 
         vertex.size = psize[names(V(i$graph))])
  })
par(mfrow = c(1, 1))

igraph::union(pops$graph[[1]], pops$graph[-1]) %>% 
  plot(., vertex.size = psize[names(V(.))],
       layout = layout_as_star(., center = "MI"))
```
